When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-04 presentation/inbreeding.Rmd
Small tweaks -- presentation moved to 4 APR

@@

>>>>

## Selection against inbreeding

![](images/par_vs_off.png)

**Selection against being inbred does not necessarily imply selection against inbreeding**

<span style="font-size: 18px;">
Reid, JM et al. (2015). *Evolution* [69:2846-2861](https://doi.org/10.5061/dryad.0015b).
</span>

@@

## Other stuff to do

Make point about inbreeding adjustment given strong constraints

Make point that it's hard to detect through a change in kinship (and subject to bias)

Make point that pre, post and polyandry evolve given strong ID and no costs

Make point that opportunity for post-cop greatly increases polyandry selection

Make point that selection tends to go with the least costly IA route
